\huge \heiti{基于遗传退火算法的网络流选址问题}

### 2018-02-26 Paper/main.tex
完成中文摘要

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  中文摘要
%  调整摘要、关键词，中图分类号的页边距
%  中英文同时调整
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setlength{\oddsidemargin}{1cm} % 3.17cm - 1 inch
\setlength{\evensidemargin}{\oddsidemargin}
\setlength{\textwidth}{13.50cm}
\vspace{-.8cm}
\begin{center}
	\parbox{\textwidth}
	{\textbf{摘~~~要} \quad ~{\kaishu  to do。}\\
	\textbf{关键词} \quad {\kaishu 网络流, 选址, 遗传算法, 退火算法，启发式算法}
	%\\ \textbf{中图分类号}\quad TP391.4\qquad  \textbf{文献标识码}\quad A\
}
\end{center}

@@

	{\small{\textbf{Abstract}\quad to do.\\
	\textbf{Key Words}\quad Network Flow, Location, Genetic Algorithm, Annealingg Algorithm, Heuristic Algorithm}}
}
\end{center}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  中文摘要
%  调整摘要、关键词，中图分类号的页边距
%  中英文同时调整
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setlength{\oddsidemargin}{1cm} % 3.17cm - 1 inch
\setlength{\evensidemargin}{\oddsidemargin}
\setlength{\textwidth}{13.50cm}
\vspace{-.8cm}
\begin{center}
	\parbox{\textwidth}
	{\textbf{摘~~~要} \quad ~{\kaishu 本文旨在解决网络流中的选址问题，即在拓扑网络中，链路代价和流量上限已知，通过启发式算法确定合适的设施选址问题来得到较少的费用。遗传算法按照适者生存和优胜劣汰的原则，逐代产生更好的解，并通过交叉、变异来产生新的个体。模拟退火算法会概率性的接收恶化解来跳出局部最优。本文采用的启发式算法将遗传算法和模拟退火算法结合，并通过计算多源多汇网络流费用与设施费用之和作为计算适应度的因素，得到了不错的结果。}\\
	\textbf{关键词} \quad {\kaishu 网络流, 选址, 遗传算法, 退火算法，启发式算法}
	%\\ \textbf{中图分类号}\quad TP391.4\qquad  \textbf{文献标识码}\quad A\
}
\end{center}

@@

	{\small{\textbf{Abstract}\quad This paper aims to solve the problem of location in network flow, that is, in topological networks, the upper limit of link cost and traffic is known, and the heuristics can be used to determine the appropriate facility location problem to get less cost. According to the principle of survival of the fittest and the survival of the fittest, genetic algorithms generate better solutions one by one, and generate new individuals through crossover and mutation. Simulated annealing algorithm will receive the worst solution to jump out of the local optimum. The heuristic algorithm used in this paper combines genetic algorithm and simulated annealing algorithm, and obtains the good result by calculating the sum of the cost of multi-source multi-sink network flow and facility cost as the factor of calculating fitness.\\
	\textbf{Key Words}\quad Network Flow, Location, Genetic Algorithm, Annealingg Algorithm, Heuristic Algorithm}}
}
\end{center}
